---
title: "flight_delay"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{flight_delay}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(BonusLab)
library(dplyr)
library(nycflights13)

ridgereg <- getFromNamespace("ridgereg", "BonusLab")
```


1. Read in the weather dataset and the flights dataset from the nycflights13 package and remove eventual variables you do not believe to have a predictive value.
```{r}

data(flights, package="nycflights13", envir = environment())
data(weather, package="nycflights13", envir = environment())

# remove variables
flights <- as.data.frame(flights)
flights <- flights[,c(6,9,13,16,19)]

weather <- as.data.frame(weather)
weather <- weather[,c(1,6,7,8,9,12,14,15)]

```


2. Add extra weather data from the weather dataset and create interaction effects you think could be of interest for the prediction.
```{r}

data_flights_weather <- flights %>%
    dplyr::left_join(weather, by = c("time_hour" = "time_hour", "origin" = "origin"))
data_flights_weather <- data_flights_weather[,-c(3,5)]


# create interaction effects - might be interesting for prediction

# arr_delay
data_arr <- data_flights_weather[!is.na(data_flights_weather$arr_delay),]
data_arr <- data_arr[,-1]
data_arr <- na.omit(data_arr)

null_model <- lm(arr_delay ~ 1, data = data_arr)
saturated_model <- lm(arr_delay ~ .^2, data = data_arr)

## takes very long to run
# best_model <- MASS::stepAIC(null_model, direction = "both",
#                             scope = list(lower = null_model, 
#                                          upper = saturated_model), trace = FALSE)
# summary(best_model)

# visib:temp + humid:temp + 
# humid:distance + distance:temp


# dep_delay
data_dep <- data_flights_weather[!is.na(data_flights_weather$dep_delay),]
data_dep <- data_dep[,-2]
data_dep <- na.omit(data_dep)

null_model <- lm(dep_delay ~ 1, data = data_dep)
saturated_model <- lm(dep_delay ~ .^2, data = data_dep)

## takes very long to run
# best_model <- MASS::stepAIC(null_model, direction = "both",
#                             scope = list(lower = null_model,
#                                          upper = saturated_model), trace = FALSE)
# summary(best_model)

# humid:precip, dewp:distance
# precip:visib, precip:dewp 

```



3. Use the caret package to divide the flight dataset into three sets: test, train and validation (with the proportions 5%, 80% and 15%.
```{r}

## arr_delay
train_indices <- caret::createDataPartition(data_arr$arr_delay, times = 1,
                                     p = 0.8, list = FALSE, groups = 2)

# create training set
train_data_arr <- data_arr[train_indices,]


remaining_data <- data_arr[-train_indices,]

validation_indices <- caret::createDataPartition(remaining_data$arr_delay,
                                          times = 1, p = 0.75, list = FALSE, groups = 2)

# create validation set
validation_data_arr  <- remaining_data[validation_indices,]

# create test set
test_data_arr <- remaining_data[-validation_indices,]

```

```{r}

## dep_delay
train_indices <- caret::createDataPartition(data_dep$dep_delay, times = 1,
                                     p = 0.8, list = FALSE, groups = 2)

# create training set
train_data_dep <- data_dep[train_indices,]


remaining_data <- data_dep[-train_indices,]

validation_indices <- caret::createDataPartition(remaining_data$dep_delay,
                                          times = 1, p = 0.75, list = FALSE, groups = 2)

# create validation set
validation_data_dep  <- remaining_data[validation_indices,]

# create test set
test_data_dep <- remaining_data[-validation_indices,]

```


4. Train ridge regressions models for different values of lambda and evaluate the root mean squared error (see here https://heuristically.wordpress.com/2013/07/12/calculate-rmse-and-mae-in-r-and-sas/)
on the validation set. Try to find an optimal value for lambda.
```{r}

# didn't had enough time for that


```


5. When you found a good value for lambda, use this to predict the test set and report the RMSE of your predicted model.
```{r}

# didn't had enough time for that



```





