---
title: "ridgereg_vignette"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{ridgereg_vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(BonusLab)
```

Most of this information is available scattered throughout the R documentation. This appendix brings it all together in one place. 

This R function is created to handle linear regression models. With the [ridgereg] package a ridge regression model is created. The function takes three arguments formula, data and lambda and returns an object of class [ridgereg]. Special functions such as `print()`, `pred()` and `coef()` can be used to get more information about the model. 

## simple example
We'll start by creating a simple ridge regression model. 

### load data
First load the data you want to analyse. In this vignette the well known dataset `iris` is used for demonstration. 
```{r}
data("iris")
```


### create linear regression model
In the next step we call our class [ridgereg] with the arguments formula = Petal.Length~Sepal.Width+Sepal.Length, data = iris and lambda = 0.01. We save the returned ridgereg-object in the variable mod_object. 
```{r}
ridgereg <- getFromNamespace("ridgereg", "BonusLab")
mod_object <- ridgereg(Petal.Length~Sepal.Width+Sepal.Length, data = iris, lambda = 0.01)
```

# use functions
In the next step we can now use the different functions to get a better insight into our ridge regression model. 

1. `$print()`
The `$print()` functions gives us the coefficients and coefficient names of our model. 
```{r}
mod_object$print()
```

2. `$pred()`
The `$pred()` functions gives us the predicted response values (\hat{y}) of the model. 
```{r}
mod_object$pred()
```


3. `$coef()`
The `$coef()` functions gives us the coefficients of the model as a names vector. 
```{r}
mod_object$coef()
```

